Minimizing post-shock forecasting error through aggregation of outside information

### 2021-01-28 Revision/manuscript.tex
revised manuscript and list with changes in red, and created separate checklist

\red{Check out this paragraph.} In our methodological framework, the researcher first creates a donor pool of time series which have undergone similar structural shocks in the past. Similarity in this context refers to the shock effects as arising from a common distribution with existing second moments. The unobserved shock effect in the time series of interest is assumed to arise from the same distribution. Construction of the donor pool and the desired aims of the donor pool has precedent in synthetic control methodology (SCM) \citep{abadie2010synthetic}. As in SCM, care is needed when forming the donor pool of time series. However, there are several key differences between our framework and SCM. Unlike in SCM, we are not trying to estimate the causal effect of an intervention. Also, we assume that the time series forming the donor pool are independent from the time series under study before the timing of the shock. This rules out panel data applications where the time series of interest and those forming the donor pool evolve in tandem. When there are large time differences between the time series under study and those forming the donor pool, then the dependence will be negligible in practice. This is the case in the Conoco Phillips and Apple stock forecasting examples.

@@

In this article, we will assume a simple autoregressive data generating process  with a general random-effect structure. These specifications are similar to the ``$K$ latent pooling'' framework of \cite{ramaswamy1993empirical}. However, our model formulation is more general than \cite{ramaswamy1993empirical}. In our model, the donor pool can consist of dependent time series, but the time series forming the donor pool are required to be independent from the time series of interest. However, mutual independence among time series in the donor pool can aid prospective evaluation of the reliability of our method. We consider three aggregation techniques: simple averaging, inverse-variance weighted averaging, and similarity weighting. The latter technique is similar to the weighting in SCM \citep{abadie2010synthetic}. The considered adjustment strategies all target the mean of the shock effect distribution. Such an estimation strategy can reduce mean squared error (MSE) when variation in the shock effect distribution is small relative to the mean. We provide risk-reduction propositions that detail the conditions when the adjusted forecasts will work better than the original forecast. The involved parameters in the risk-reduction propositions can be estimated by a residual bootstrap procedure that we develop. We also motivate a simple leave-one-out cross validation procedure which can prospectively assess the performance of our shock effect adjustment estimators. This prospective assessment does not require the observation of the post-shock response. Our Monte Carlo simulation results show that the risk-reduction propositions are nearly perfectly correct when the model for the shock effects is identified well with appropriate covariates under a fixed design.  We demonstrate the utility of our methodology with two real data analyses. The first of these focuses on forecasting the stock price of Conoco Phillips after March 9th, 2020, in the midst of the COVID-19 pandemic and an oil supply war. The second of these focuses on forecasting the stock price of Apple Inc. after the company releases their latest installment of the MacBook on November 10th, 2020. We will show that our proposed adjustment estimators yield much better results than no adjustment in these examples. The Conoco Phillips example provides an empirical application of our methods when the shock is unprecedented in nature, arising from a global pandemic and an oil supply shock. The Apple example provides a case for post-shock prediction when the shock has precedent, Apple just released the latest version of their MacBook product. We now elaborate our framework for post-shock prediction.

@@

In our framework we have assumed the covariates to be known. However, it may be the case that the shock effects the covariates as well as the response. If so, one may be able to consider forecast scenarios (or conditional forecasts) \citep{baumeister2014real} to make post-shock predictions. In this setting, one would need to produce a grid of likely $\mathbf{x}_{1, T_1^* + 1}$ values to proceed. A post-shock prediction can be made for every hypothetical $\mathbf{x}_{1, T_1^* + 1}$ value forming the previously mentioned grid. This yields a range of post-shock predictions whose validity is subject to the accuracy of the $\mathbf{x}_{1, T_1^* + 1}$ values forming the grid. This may gives users a sense of the variability of post-shock predictions due to forecast error from covariates that are also affected from the shock.

@@

Construction of the donor pool is a critical step in our post-shock prediction framework. In our model, shocks from candidate time series in the donor pool, together with the shock in the time series of interest, should come from a family of distributions that allow for varying variances and  varying means that are linear functions of common covariates. However, it may be difficult to confirm such an assumption or modeling structure in practice. Also note that we assume that the time series under study is independent of those forming the donor pool, independence being practically satisfied when the time series of interest is separated from the donor pool in time. In principle, one should select time series that come from a common population, the same population as the individual under study, to form the donor pool. This selection criterion is often adopted in the literature of comparative case studies. For example, \citet{card1990impact} used a set of cities in southern U.S. to estimate the effect of 1980 Mariel Boatlift on the Miami labor market. \citet{abadie2003economic} utilized a donor pool of two Spanish regions to approximate the effect of terrorism on  the economic growth of Baseque Country. To estimate the effect of Proposition 99, a large tobacco control program in California  in 1988, on the annual per-capita cigarette sales of 2000, \cite{abadie2010synthetic} constructed a donor pool consisting of US states, which did not implement \emph{any} large-scale tobacco control program during their sampling period. Common features of those studies are that they all carefully constructed the donor pool and discarded any suspicious outliers.

>>>>

In our methodological framework, the researcher first creates a donor pool of time series which have undergone similar structural shocks in the past. \red{Similarity in this context refers to the shock effects as arising from a common distribution that has existing second moments and allows for varying variances and varying means that are linear functions of common covariates.} The unobserved shock effect in the time series of interest is assumed to arise from the same distribution. Construction of the donor pool and the desired aims of the donor pool has precedent in synthetic control methodology (SCM) \citep{abadie2010synthetic}. As in SCM, care is needed when forming the donor pool of time series. However, there are several key differences between our framework and SCM. Unlike in SCM, we are not trying to estimate the causal effect of an intervention. Also, we assume that the time series forming the donor pool are independent from the time series under study before the timing of the shock. This rules out panel data applications where the time series of interest and those forming the donor pool evolve in tandem. When there are large time differences between the time series under study and those forming the donor pool, then the dependence will be negligible in practice. This is the case in the Conoco Phillips and Apple stock forecasting examples.

@@

In this article, we will assume a simple autoregressive data generating process  with a general random-effect structure. These specifications are similar to the ``$K$ latent pooling'' framework of \cite{ramaswamy1993empirical}. However, our model formulation is more general than \cite{ramaswamy1993empirical}. In our model, the donor pool can consist of dependent time series, but the time series forming the donor pool are required to be independent from the time series of interest. However, mutual independence among time series in the donor pool can aid prospective evaluation of the reliability of our method. We consider three aggregation techniques: simple averaging, inverse-variance weighted averaging, and similarity weighting. The latter technique is similar to the weighting in SCM \citep{abadie2010synthetic}. The considered adjustment strategies all target the mean of the shock effect distribution. Such an estimation strategy can reduce mean squared error (MSE) when variation in the shock effect distribution is small relative to the mean. We provide risk-reduction propositions that detail the conditions when the adjusted forecasts will work better than the original forecast. The involved parameters in the risk-reduction propositions can be estimated by a residual bootstrap procedure that we develop. We also motivate a simple leave-one-out cross validation procedure which can prospectively assess the performance of our shock effect adjustment estimators. This prospective assessment does not require the observation of the post-shock response. Our Monte Carlo simulation results show that the risk-reduction propositions are nearly perfectly correct when the model for the shock effects is identified well with appropriate covariates under a fixed design.  We demonstrate the utility of our methodology with two real data analyses. The first of these focuses on forecasting the stock price of Conoco Phillips after March 9th, 2020, in the midst of the COVID-19 pandemic and an oil supply war. The second of these focuses on forecasting the stock price of Apple Inc. after the company releases their latest installment of the MacBook on November 10th, 2020. We will show that our proposed adjustment estimators yield much better results than no adjustment in these examples. The Conoco Phillips example provides an empirical application of our methods when the shock is unprecedented in nature, arising from a global pandemic and an oil supply shock. \red{The Apple example is about annual release of their MacBook products, and provides a case for post-shock prediction when the shock has precedent.} We now elaborate our framework for post-shock prediction.

@@

In our framework we have assumed the covariates to be known. However, it may be the case that the shock \red{affects} the covariates as well as the response. If so, one may be able to consider forecast scenarios (or conditional forecasts) \citep{baumeister2014real} to make post-shock predictions. In this setting, one would need to produce a grid of likely $\mathbf{x}_{1, T_1^* + 1}$ values to proceed. A post-shock prediction can be made for every hypothetical $\mathbf{x}_{1, T_1^* + 1}$ value forming the previously mentioned grid. This yields a range of post-shock predictions whose validity is subject to the accuracy of the $\mathbf{x}_{1, T_1^* + 1}$ values forming the grid. This may gives users a sense of the variability of post-shock predictions due to forecast error from covariates that are also affected from the shock.

@@

Construction of the donor pool is a critical step in our post-shock prediction framework. In our model, shocks from candidate time series in the donor pool, together with the shock in the time series of interest, should come from \red{the same distribution that allows} for varying variances and  varying means that are linear functions of common covariates. However, it may be difficult to confirm such an assumption or modeling structure in practice. Also note that we assume that the time series under study is independent of those forming the donor pool, independence being practically satisfied when the time series of interest is separated from the donor pool in time. In principle, one should select time series that come from a common population, the same population as the individual under study, to form the donor pool. This selection criterion is often adopted in the literature of comparative case studies. For example, \citet{card1990impact} used a set of cities in southern U.S. to estimate the effect of 1980 Mariel Boatlift on the Miami labor market. \citet{abadie2003economic} utilized a donor pool of two Spanish regions to approximate the effect of terrorism on  the economic growth of Baseque Country. To estimate the effect of Proposition 99, a large tobacco control program in California  in 1988, on the annual per-capita cigarette sales of 2000, \cite{abadie2010synthetic} constructed a donor pool consisting of US states, which did not implement \emph{any} large-scale tobacco control program during their sampling period. Common features of those studies are that they all carefully constructed the donor pool and discarded any suspicious outliers.
